23-Figure2-051321

### 2021-06-01 notebooks/02-Figure2-051321.Rmd
adjusted network legends

plot_density_prs <- 			# 
    function
(
 	df , x , xlab= 'Effectiveness', ylab='Density', coord_trans='log10', linesize = 1
)
{
    color_pal <- c('#00BFC4','#F8766D')
dens_plot <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= df%>%filter(group=='real'),
               aes(x={{x}} ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= df%>%filter(group=='random'),
               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),linetype='dashed',
               stat = 'density' ,show.legend=F)+#, binwidth = 0.1) + 
    geom_vline(data= df%>%filter(group=='real')%>%mutate(g = T),aes(xintercept = mean({{x}}), linetype='Real'),color=color_pal[1],size=linesize, show.legend=NA)+
    geom_vline(data= df%>%filter(group=='random')%>%mutate(g = F),aes(xintercept = mean({{x}}),linetype='Random', group=random_id),color=color_pal[2], size=linesize,show.legend=NA)+
    scale_linetype_manual(name = "Limits", labels = c("real", "random"), values = c("Real" = 3, "Random" = 3)) +
    guides(colour=guide_legend(override.aes = list(linetype=1)),
           linetype=guide_legend(override.aes=list(colour=color_pal)))+
    theme_bw()+
    ylab(ylab)+
    xlab(xlab)+
    coord_trans(x = coord_trans)+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
    scale_color_discrete(labels=c('Rewired\nnetworks','PSN'))+
theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
dens_plot
}

@@

# Figure2 A,B
```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2
)
deg_scatter_plots
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
```

@@

>>>>

plot_density_prs <- 			# 
    function
(
 	df , x , xlab= 'Effectiveness', ylab='Density', coord_trans='log10', linesize = 1
)
{
    color_pal <- c('#00BFC4','#F8766D')
dens_plot <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= df%>%filter(group=='real'),
               aes(x={{x}} ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= df%>%filter(group=='random'),
               aes(x={{x}} ,y=..scaled..,fill=random_id, color=group),linetype='dashed',
               stat = 'density' ,show.legend=F)+#, binwidth = 0.1) + 
    geom_vline(data= df%>%filter(group=='real')%>%mutate(g = T),aes(xintercept = mean({{x}}), linetype='Real'),color=color_pal[1],size=linesize, show.legend=NA)+
    geom_vline(data= df%>%filter(group=='random')%>%mutate(g = F),aes(xintercept = mean({{x}}),linetype='Random', group=random_id),color=color_pal[2], size=linesize,show.legend=NA)+
    scale_linetype_manual(name = "Limits", labels = c("real", "random"), values = c("Real" = 3, "Random" = 3)) +
    guides(colour=guide_legend(override.aes = list(linetype=1)),
           linetype=guide_legend(override.aes=list(colour=color_pal)))+
    theme_bw()+
    ylab(ylab)+
    xlab(xlab)+
    coord_trans(x = coord_trans)+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
    scale_color_discrete(labels=c('Rewired\nnetworks','PSN'))+
theme(legend.text = element_text(margin = margin(b = 10)), panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
dens_plot
}
```

@@

# Figure2 A,B
```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2
)
deg_scatter_plots
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
print(cor.test(pcc_df$deg[pcc_df$deg<10],pcc_df$sens[pcc_df$deg<10],method='spearman',exact=FALSE))
```

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)
}
```
